Verifying Demonstrations

### 2017-08-23 properties.tex
Edits properties

\Cref{CountOnce} is required to prevent Sybil attacks.
I.e.\ that one individual can provide two proofs of participation and thus be 
counted twice, this situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
This can be done by including a signature made by a verified key.

There might be the case that there is also a counter protest at the same time, 
these would have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated (\cref{DesignatedEvent}).
This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
its \enquote{manifesto}.

@@

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.

@@

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
I.e.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

@@

We also have an architectural problem.
If the system is only run by volunteering activists, then Eve can simply 
analyse network traffic to detect who is running nodes in the system.

@@

We would still have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.

>>>>

\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
individual can provide two proofs of participation and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
This can be done by including a signature made by a verified key.
(We will discuss the privacy aspects in \cref{Privacy}.)

\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
protest at the same time and place, these would have the same spatial and 
temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
its \enquote{manifesto}.

@@

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.
This is fine, since we do not want to catch any cheater, we just do not want to
count them more than once.

@@

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

@@

We also have an architectural problem.
If the system is only run by volunteering activists, then Eve can simply 
analyse network traffic and look for people running nodes in the system.

@@

Similarly, we have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.
Otherwise Eve can analyse the network traffic to find out who submitted proofs 
to the system.
